---
title: "Xenopus tropicalis Stage 11 RNA+ATAC multiome analysis"
output: html_document
---

This notebook is a narrative entry point to the modular pipeline. The underlying analysis
lives in `scripts/` so the same code can be run non-interactively and version controlled.

```{r setup, message=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = TRUE, message = TRUE)
source("../scripts/00_setup.R")
```

## Build multimodal object

```{r create-object}
source("../scripts/01_create_multiome_object.R")
```

## Quality control

```{r qc}
source("../scripts/02_qc_filtering.R")
```

## RNA processing

```{r rna}
source("../scripts/03_rna_processing.R")
```

## ATAC processing

```{r atac}
source("../scripts/04_atac_processing.R")
```

## WNN integration and clustering

```{r integration}
source("../scripts/05_wnn_integration.R")
source("../scripts/06_clustering.R")
```

## Expression-based annotation

```{r annotation}
source("../scripts/07_expression_annotation.R")
source("../scripts/08_annotation_validation.R")
```

## Optional chromatin visualization and links

These are controlled by `RUN_COVERAGE_PLOTS` and `RUN_PEAK_GENE_LINKS` in
`config/analysis_config.R`.

```{r optional-atac}
source("../scripts/09_coverage_plots.R")
source("../scripts/10_peak_gene_links.R")
```

## Finalize

```{r finalize}
source("../scripts/11_finalize.R")
```
